---
title: "Visualization_1"
author: "Emma Warshaw"
date: "2022-09-29"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggridges)
```
This code from the course website


```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's make a scatterplot: 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))
```
Run this and end up with a blank plot
There are 3 things to define: data set and aesthetic mappings.  It's done that and completed a basic plot but we haven't added any geometry to have stuff on the plot.  At `geom_plot` to get the stuff: 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

Let's make the same scatterplot, but different: You can use a piping structure to pipe in the geometry.  This is useful you want to do some stuff to the data before you put it on a plot without making more lines of code. 
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Keep making the same plot but different: you can create ggplot objects and save them, then add them into a whatever base plot you made and add in the geometries.  It's a way to superimpose the geometry on a base plot for you don't have to keep recreating plots. 
```{r}
plot_weather = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) 

plot_weather + geom_point()
```

#Let's make it fancy!

This will colocode the plot based on the 'name' variable in the data set. aes=aesthetic 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```

Let's add a new aesthetic with  `geom_smooth`.  This runs a curve through the data set that will describe the association. This is cool, but it gives one curve for the 3 different weather stations.  We've applied the curve to the scatterplot only.  Apply it in ggplot to get lines for each individual weather station.  
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) +
  geom_smooth(se = FALSE)

ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE)
```

The alpha value dictates transparency in the plots.  Closer to one is not transparent at all, while closer to zero is very transparent 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .3) +
  geom_smooth(se = FALSE)  
```

Separate the plot by variable to make it more readable.  We do this with a `facet` command. The data in the parentheses of facet defines the row and column variables.  Put in a period to not define by anything, and R will map it as it works.  
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .3) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

Play around with the aesthetics when you add in precipitation in the geometry. 
```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_smooth(se = FALSE) 
```

```{r}
ggplot(weather_df, aes(x = tmax, y = tmin)) + 
  geom_hex()
```

```{r}
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin), color = "blue")
ggplot(weather_df) + geom_point(aes(x = tmax, y = tmin, color = "blue"))
```

Make a histogram: not defining anything on the y-axis because it's just going to scale as necessary
```{r}
ggplot(weather_df, aes(x = tmax)) + 
  geom_histogram()
```

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram(position = "dodge", binwidth = 2)
```

More options: density plot that gives you a kind smoothed-over histogram 
```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_density(alpha = .4, adjust = .5, color = "blue")
```

Box plots: Have to define the values for both the x and y axis.  
```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + geom_boxplot()
```

Violin Plot: Tells you the same kind of stuff that a box plot gives you, but adds in the distribution instead of the IQR like we see in a boxplot. 
```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), alpha = .5) + 
  stat_summary(fun = "median", color = "blue")
```

Ridge Plot: Creates each density but stacks them up next to each other instead of the weird overlay that comes out of a violin plot. This is much nicer if you need to compare distributions for a ton of categories.  
```{r}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges(scale = .85)
```

#Saving and imbedding plots

First make a plot. Then save it with `ggplot`, giving it a name in parentheses followed by the name of the plot you just made, followed by width and height values for the output.  You can also add in a file="" command with a directory in there to tell it where to save.     
```{r}
weather_plot = ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .5) 

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5)
```


```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```

